SiO Molecular Jets around young stars - A numerical perspective

### 2013-07-15 PAPER/ms_final_bv.tex
Added eta3 for molecular run

\section{Introduction}

@@

The jet enters into the medium through a nozzle of radius $R_{\rm jet}$
from the lower boundary (z = 0). The jet density is fixed to
be $10^{5} \rm cm^{-3}$ and it has a radius of $2.5\times10^{15} \rm cm \sim
167\,AU$. The jet is injected into the domain with a typical 
velocity of $v_{\rm jet,0}$ = 100 km/s as is the case for most low mass stellar jets
specially the low velocity component. The constant jet velocity is
superimposed with periodic pulsation of the form,
\begin{equation}
v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(t/T_{\rm p}))
\end{equation}
where the amplitude A is 0.25 and time period $T_{\rm p} = 10$
years. The pressure at the surface of the jet is $10^{-10} \rm
dyne\,\,cm^{-2}$ corresponding to a temperature of $T_{\rm jet} \sim
4\times10^{3}\,K$. Inside the jet beam, a radial variation of thermal
and magnetic pressure is adopted to maintain a magneto-static
equilibrium. We adopt the
same radial profiles used by \cite{Stone:2000p2650} for all our runs. 
Based on these profiles, the toroidal magnetic field is assumed to be
zero at the axis and achieves a maximum at some radius, $r_{\rm m}$
inside the jet. The maximum value, $B_{\phi,\rm m}$, depends on the
plasma $\beta$ which is a parameter used for our study along with the
density contrast $\eta$.
%

@@

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{grid}
\end{figure*}
\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 5 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}

>>>>

\section{Introduction} 
Interaction of jet with ambient medium , Class 0 sources, momentum and
energy injection, High mass and low mass outflows \\

Observations of Outflows in CO and SiO in mm, H2 in IR, Optical jets
HH objects, syncrotron emission \\

Molecules from jet driven or wind driven, Interesting features like
EHV, low velocity component etc, list interesting outflows from Class 0 \\

Attempts of simulations either only dynamics with analytic approaches
to compare observational features, or only chemistry to estimate
abundances. The reality lies in the middle!\\

Combine dynamics of MHD jet with molecular chemistry and comparing
with observations via post-processing simulations with line radiative
transfer codes. \\

Paper Layout \\

@@

The jet enters into the medium through a nozzle of radius $R_{\rm jet}$
from the lower boundary (z = 0). The jet density is fixed to
be $10^{5} \rm cm^{-3}$ and it has a radius of $2.5\times10^{15} \rm cm \sim
167\,AU$. The jet is injected into the domain with a typical 
velocity of $v_{\rm jet,0}$ = 100 km/s as is the case for most low mass stellar jets
specially the low velocity component. The constant jet velocity is
superimposed with periodic pulsation of the form,
\begin{equation}
v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(2.0\pi t/T_{\rm p}))
\end{equation}
where the amplitude A is 0.25 and time period $T_{\rm p} = 70$
years. The pressure at the surface of the jet is $10^{-10} \rm
dyne\,\,cm^{-2}$ corresponding to a temperature of $T_{\rm jet} \sim
4\times10^{3}\,K$. Inside the jet beam, a radial variation of thermal
and magnetic pressure is adopted to maintain a magneto-static
equilibrium. We adopt the
same radial profiles used by \cite{Stone:2000p2650} for all our runs. 
Based on these profiles, the toroidal magnetic field is assumed to be
zero at the axis and achieves a maximum at some radius, $r_{\rm m}$
inside the jet. The maximum value, $B_{\phi,\rm m}$, depends on the
plasma $\beta$ which is a parameter used for our study along with the
density contrast $\eta$.
%

@@

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{grid}
\end{figure*}

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/molcjet_510.png}
 \caption{Fraction of hydrogen species in the run with molecular
   cooling having $\eta$ = 5 and $\beta$ = 10.}
\label{grid}
\end{figure*}

\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 5 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}
